Programming Distributed Control Planes

### 2016-01-17 paper/language.tex
added syntax figure to paper

>>>>

% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}

\begin{figure*}
  \begin{minipage}[t]{.42\linewidth}
  \hdr{\large Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline
     pol &::=& c_1, \dots, c_n & \textit{constraints} \\
     c   &::=& p \Rightarrow r_1 \gg \dots \gg r_m & \textit{preferences} \\
     p   &::=& true & \textit{true} \\
      &\BNFALT& \neg p & \textit{negation} \\
      &\BNFALT& p_1 \vee p_2 & \textit{disjunction} \\
      &\BNFALT& p_1 \wedge p_2 & \textit{conjunction} \\
      &\BNFALT& prefix = x & \textit{prefix test} \\
      &\BNFALT& comm = t & \textit{community test} \\
     r   &::=& n & \textit{AS number} \\
      &\BNFALT& in & \textit{internal loc} \\
      &\BNFALT& out & \textit{external loc} \\
      &\BNFALT& r_1 \cup r_2 & \textit{union} \\
      &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
      &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
      &\BNFALT& !(r) & \textit{path negation} \\
      &\BNFALT& r^* & \textit{repetition} \\
  \end{array} \]

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Propane Macros}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rcl}
    \hline
    only(X)       & = & X^* \\
    never(X)      & = & (!X)^* \\
    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
    upstream(X)   & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
    downstream(X) & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
    end(X)        & = & (out^* \cdot in^* \cdot (X \cap in)) \cup \\
                  & = & (out^* \cdot in^+ \cdot out^* \cdot (X \cap out)) \\
    start(X)      & = & ((X \cap in) \cdot in^* \cdot out^*) \cup \\
                  & = & ((X \cap out) \cdot out^* \cdot in^+ \cdot out^*) \\
    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
    link(X,Y)     & = & (out^* \cdot in^* \cdot X \cdot Y \cdot in^* \cdot out^*) \cup \\
                  & = & (out^* \cdot (X \cap out) \cdot (Y \cap in) \cdot in^* \cdot out^*) \cup \\
                  & = & (out^* \cdot in^* \cdot (X \cap in) \cdot (Y \cap out) \cdot out^*) \\
  \end{array} \]

  \end{minipage}

  \hrulefill

  \caption{Regular Intemediate Language (RIL) syntax (left), and 
           Propane language expansions (right).}
  \label{fig:semantics}
\end{figure*}
